### 2022-01-27 src/text/1-introduction.tex
Adapt tex files
Reformat tex files

\section{Introduction}
\label{sec:intro}

@@

Gamma-ray astronomy is a rather young field of research.
By detecting and reconstructing arrival direction, time and energy
of primary cosmic gamma-rays
The gamma-ray sky is either observed by ground based instruments

, driven by experiments with proprietary software often based
on ROOT, because of the particle physics background. Such 
as HESS, Veritas or Magic.

@@

Once the primary photons are reconstructed the format of the data
of all Gamma-ray instrumets can be brought into a common format.
An effort is the gamma-astro data formats \cite{gadf-zenodo}.
The data format is based on FITS  \citep{fits}.

@@

Astronomical data analysis software written in Python existed since 2000.
e.g. sherpa \citep{sherpa-2011, sherpa-2009}, or for gamma-ray even
PyFACT \citep{pyfact}.

The short-term success of Pythion lead to a prolifaration of packages, until
\astropy \citep{astropy} was created in 2012. Astropy is and

Gammapy is a Python package for gamma-ray astronomy.

@@

\begin{itemize}
\item Gammapy webpage\footnote{\GammapyUrl}
\item Naima\footnote{\NaimaUrl} \citep{Naima}
\item Gammapy use in science publications: \citep{Owen2015}, SNR shell, HGPS
\end{itemize}

@@

\begin{figure}[t]
\centering
\includegraphics[height=0.5\textwidth, angle=270]{figures/gammapy-big-picture}
\caption{
Gammapy is a Python package for high-level gamma-ray data analysis. Using event
lists, exposures and point spread functions as input you can use it to generate
science results such as images, spectra, light curves or source catalogs. So far
it has been used to simulate and analyse H.E.S.S., CTA and \textit{Fermi}-LAT
data, hopefully it will also be applied to e.g. VERITAS, MAGIC or HAWC data in
the future.
}
\label{fig:big-picture}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics[width=0.5\textwidth]{figures/gammapy-dependencies}
\caption{
The Gammapy stack. Required dependencies Numpy and Astropy are illustrated with
solid arrows, optional dependencies (the rest) with dashed arrows.
}
\label{fig:dependencies}
\end{figure}

>>>>

\section{Introduction}
\label{sec:introduction}

@@

Gamma-ray astronomy is a rather young field of research. By detecting and
reconstructing arrival direction, time and energy of primary cosmic gamma-rays
The gamma-ray sky is either observed by ground based instruments, driven by
experiments with proprietary software often based on ROOT, because of the
particle physics background. Such as HESS, Veritas or Magic.

@@

Once the primary photons are reconstructed the format of the data of all
Gamma-ray instrumets can be brought into a common format. An effort is the
gamma-astro data formats~\cite{gadf-zenodo}. The data format is based on FITS
\citep{fits}.

@@

Astronomical data analysis software written in Python existed since 2000. e.g.,
sherpa~\citep{sherpa-2011, sherpa-2009}, or for gamma-ray even PyFACT
\citep{pyfact}.

The short-term success of Pythion lead to a prolifaration of packages, until
\astropy~\citep{astropy} was created in 2012. Astropy is and Gammapy is a
Python package for gamma-ray astronomy.

@@

\begin{itemize}
	\item Gammapy webpage\footnote{\GammapyUrl}
	\item Naima\footnote{\NaimaUrl}~\citep{Naima}
	\item Gammapy use in science publications:~\citep{Owen2015}, SNR shell, HGPS
\end{itemize}

@@

\begin{figure}[t]
	\centering
	\includegraphics[height=0.5\textwidth, angle=270]{static/gammapy-big-picture}
	\caption{
		Gammapy is a Python package for high-level gamma-ray data analysis. Using event
		lists, exposures and point spread functions as input you can use it to generate
		science results such as images, spectra, light curves or source catalogs. So
		far it has been used to simulate and analyse H.E.S.S., CTA and
		\textit{Fermi}-LAT data, hopefully it will also be applied to e.g., VERITAS,
		MAGIC or HAWC data in the future.
	}
	\label{fig:big-picture}
\end{figure}

\begin{figure}[t]
	\centering
	\includegraphics[width=0.5\textwidth]{static/gammapy-dependencies}
	\caption{
		The Gammapy stack. Required dependencies Numpy and Astropy are illustrated with
		solid arrows, optional dependencies (the rest) with dashed arrows.
	}
	\label{fig:dependencies}
\end{figure}

### 2022-01-27 src/text/4-project.tex
Reformat tex files

\section{Gammapy project}
\label{sec:project}

@@

\subsection{Development, testing}

\todo{Jose Enrique writes this...}
-Github, pytest, CI, PIGs?

\subsection{Documentation}

@@

\subsection{Software distribution and user support}

- Pip, conda, versions, gammapy download

\subsection{Community}

TODO: Figure: Screenshot of Jupyter notebook or docs with notebook, could show the interactive maps view
\begin{verbatim}
m = Map.read(“diffuse.fits”)
m.plot_interactive()        
\end{verbatim}

>>>>

\section{Gammapy project}
\label{sec:gammapy-project}

@@

\subsection{Development, testing}
\label{ssec:development-testing}
\todo{Jose Enrique writes this...}
-Github, pytest, CI, PIGs?

\subsection{Documentation}
\label{ssec:documentation}

@@

\subsection{Software distribution and user support}
\label{ssec:software-distribution-and-user-support}
- Pip, conda, versions, gammapy download

\subsection{Community}
\label{ssec:community}
TODO: Figure: Screenshot of Jupyter notebook or docs with notebook, could show
the interactive maps view
\begin{verbatim}
m = Map.read(“diffuse.fits”)
m.plot_interactive()
\end{verbatim}
